A Bayesian search to find \\high-mass black holes using LIGO data

### 2020-06-24 main.tex
Committed by TeXstudio

\caption[BBH parameters corresponding to durations $<454$ ms]{\label{tab:parameters}Template Banks's parameters for templates with duration $<454$ ms.}
\centering
\begin{tabular}{lrr}
\toprule
  & Minimum & Maximmum\\
\midrule
Component Mass 1 $[\text{M}_{\odot}]$ & 31.54 & 491.68\\
Component Mass 2 $[\text{M}_{\odot}]$ & 1.32 & 121.01\\
Total Mass $[\text{M}_{\odot}]$ & 56.93 & 496.72\\
Chirp Mass $[\text{M}_{\odot}]$ & 8.00 & 174.56\\
Mass Ratio & 0.01 & 0.98\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption[BBH parameters corresponding to durations $<454$ ms]{\label{tab:parameters}Template Banks's parameters for templates with duration $<454$ ms.}
\centering
\begin{tabular}{lrr}
\toprule
  & Minimum & Maximmum\\
Component Mass 1 $[\text{M}_{\odot}]$ & 31.54 & 491.68\\
Component Mass 2 $[\text{M}_{\odot}]$ & 1.32 & 121.01\\
Total Mass $[\text{M}_{\odot}]$ & 56.93 & 496.72\\
Chirp Mass $[\text{M}_{\odot}]$ & 8.00 & 174.56\\
Mass Ratio & 0.01 & 0.98\\
\end{tabular}
\end{table}
